\clearpage
\section*{TÀI LIỆU THAM KHẢO}
\addcontentsline{toc}{section}{TÀI LIỆU THAM KHẢO}
\begin{thebibliography}{00}

\bibitem{devlin2019bert}
J. Devlin, M. Chang, K. Lee, and K. Toutanova, "BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding," in \textit{Proceedings of the 2019 Conference of the North American Chapter of the Association for Computational Linguistics (NAACL)}, Minneapolis, USA, 2019, pp. 4171--4186.

\bibitem{phobert}
D. Q. Nguyen and A. T. Nguyen, "PhoBERT: Pre-trained language models for Vietnamese," in \textit{Proceedings of the 2020 Conference on Empirical Methods in Natural Language Processing: Findings}, Online, 2020, pp. 1037--1042.

\bibitem{visobert}
5CD-AI, "ViSoBERT: A Pre-Trained Language Model for Vietnamese Social Media Text Processing," Hugging Face Model Hub, 2023. [Online].\\
Available: \url{https://huggingface.co/5CD-AI/visobert-base-cased}

\bibitem{vaswani2017attention}
A. Vaswani \textit{et al.}, "Attention Is All You Need," in \textit{Advances in Neural Information Processing Systems}, vol. 30, 2017.

\bibitem{hochreiter1997lstm}
S. Hochreiter and J. Schmidhuber, "Long Short-Term Memory," \textit{Neural Computation}, vol. 9, no. 8, pp. 1735--1780, 1997.

\bibitem{pontiki2016semeval}
M. Pontiki \textit{et al.}, "SemEval-2016 Task 5: Aspect Based Sentiment Analysis," in \textit{Proceedings of the 10th International Workshop on Semantic Evaluation (SemEval-2016)}, San Diego, USA, 2016, pp. 19--30.

\bibitem{lin2017focal}
T. Lin \textit{et al.}, "Focal Loss for Dense Object Detection," in \textit{Proceedings of the IEEE International Conference on Computer Vision (ICCV)}, Venice, Italy, 2017, pp. 2980--2988.

\bibitem{fleiss1971kappa}
J. L. Fleiss, "Measuring nominal scale agreement among many raters," \textit{Psychological Bulletin}, vol. 76, no. 5, pp. 378--382, 1971.

\bibitem{landis1977kappa}
J. R. Landis and G. G. Koch, "The Measurement of Observer Agreement for Categorical Data," \textit{Biometrics}, vol. 33, no. 1, pp. 159--174, 1977.

\bibitem{caruana1997multitask}
R. Caruana, "Multitask Learning," \textit{Machine Learning}, vol. 28, no. 1, pp. 41--75, 1997.

\end{thebibliography}
